The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-10 paper/main.tex
Added correlation outputs.

% SEng 5852 - Spring 2013 White Paper Review
\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\MakeRobust{\Call}
\setlength\parindent{0pt}

@@

\emph{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
A smal core of developers, however, seems to be a historial fact of OSS development\cite{mockus2000case,mockus2000two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site Sourceforge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changes this?\\

@@

The \textsc{store} function accepts as an input a given random repository. The purpose of this function is to persist the given repository to a database for further analysis.

@@

\subsection{Summary Statistics}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{rrrrrrr}
\hline
Variable & Mean & Min & Max & Std. Dev. \\
\hline
\input{summary_statistics}
\hline
\end{tabular}
N = 100 Repositories
\caption{GitHub Summary Statistics}
\end{center}
\end{table}

\subsection{Hypotheses}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\begin{figure}
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}
\caption{Repostitory watchers and forks}
\end{figure}

>>>>

% SEng 5852 - Spring 2013 White Paper Review
\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\MakeRobust{\Call}
\usepackage{amsmath}
\setlength\parindent{0pt}

@@

\emph{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
A smal core of developers, however, seems to be a historial fact of OSS development\cite{mockus2000case,mockus2002two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site Sourceforge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changes this?\\

@@

The \textsc{store} function accepts as an input a given random repository. The purpose of this function is to persist the given repository to a database for further analysis. Results were stored in a MySQL relational database management system.

@@

\subsection{Summary Statistics}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{rrrrrrr}
\hline
Variable & Mean & Min & Max & Std. Dev. \\
\hline
\input{summary_statistics}
\hline
\end{tabular}
N = 100 Repositories
\caption{GitHub Summary Statistics}
\label{table:summary_stats}
\end{center}
\end{table}

Table \ref{table:summary_stats} describes summary statistics of the repository variables above. The most evident feature of the result is the large variance. In fact, for the set of tested variables $A$, each variable $A_j$ is observed to have a larger standard deviation than the variable mean.
\begin{equation}
\forall j \in A \colon \overline{j} < \sigma_{j}
\label{eq:variance}
\end{equation}
All measured variables demonstrated this characteristic.

\subsection{Hypotheses}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
A correlation coefficient of \input{watcher_forks_scatterplot-correlation} was observed betwee the number of Watchers and Forks of a repository. This suggests that a correlation between Watchers and Forks exists.
\begin{figure}
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}
\caption{Repostitory watchers and forks}
\end{figure}
The data reinforces the hypothesis, as does other research in the area. Even though there are aguments that the number of Forks is the true measure of project success\cite{baudry2012towards}, the data suggests that the two measures are related. Also, \textit{Dabbish et al.} have noted that the number of Watches can be a key for others to gauge interest in a project, and thus determine if they should participate \cite{dabbish2013leveraging}. If the number of Watchers of a repository serves as a social cue for participation, even ``passive'' involvement with a project (Watching) could influence the ``active'' participation (Forking). This could possibly contribute to the correlation of the two variables.
